### 2017-03-01 ResponseToReview114203Of16-1082v1.tex

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,twocolumn]{IEEEtran}
%\documentclass[twocolumn]{IEEEtran}
\usepackage{times}
\input{pack}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{ Response to comments by Reviewer1}
\author{Chandrashekar Lakshminarayanan$^\star$, Shalabh Bhatnagar$^\star$,
 and Csaba Szepesvari$^\dagger$\thanks{$^\star$Department of Computer
Science and Automation, Indian Institute of Science, Bangalore 560012.
E-mail: $\{$chandrul, shalabh$\}$@csa.iisc.ernet.in}
\thanks{$^\dagger$Department of Computing Science, University of Alberta,
Edmonton, Alberta, Canada T6G 2E8. E-mail: csaba.szepesvari@ualberta.ca}}
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\begin{document}
\maketitle
In what follows, we present the reviewer's comment in \emph{italized} fonts and our repsonse to them in normal fonts.
\begin{enumerate}
\item \emph{
The authors have developed a deterministic way to handle LP for MDP and
also new analytic tools for error analysis. Though this article
introduces novel contributions to the field but the writing is a bit
clumsy. Explanations of the lemmas and definitions are missing (as
marked later). The authors don't provide intuition for most of the
assumptions. Since the authors have additional space, more details
should be provided.
Some of the terms in the definitions like discounted maximal inflations
are never used directly and no reasoning behind the use of Lyapunov
stability (which is a good and important part of the technique here) is
given anywhere. For a contribution of this kind such an explanation is
at least expected. So it's better if the authors give some
explanations, elongate it a bit and make it readable to someone who
isn't expert of both control and MDP, otherwise it is a very good piece
of work.
Few detailed comments are attached.
}
\textbf{Response:} We have restructured our paper and added the explanations as suggested.
\end{enumerate}

%\input{appendix}
\end{document}

### 2017-03-01 grlp.tex
adding the review directory

The operators $\Gamma$ and $\hg$ are closely related to ALP \eqref{alp} and GRLP \eqref{grlp} respectively and are only analytical tools that we will need to express our bounds and need not be computed in practice. It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}). Though we are concerned about the behaviour of $\Gamma$ and $\hg$ on the candidate value functions in the constraint set $\N$, we want them to make sense for any arbitrary $J\in \R^n$. In order to be accomplish the same, we define $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$', so as to patch $\N$ via translations and make the neighbourhood of any arbitrary $J\in \R^n$, `look' like $\N$.

@@

\subsection{Error Bounds}

>>>>

The operators $\Gamma$ and $\hg$ are closely related to ALP \eqref{alp} and GRLP \eqref{grlp} respectively and are only analytical tools that we will need to express our bounds and need not be computed in practice. It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}). At the outset we are interested in the candidate value functions in the constraint set $\N$ and want to study them using $\Gamma$ and $\hg$. However since the basis $\Phi$ contains $\one$ we make it helps our analysis to define the set $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$'.

@@

%\subsection{Error Bounds}

### 2017-03-01 prob.tex
adding the review directory

\textbf{Error Analysis of ALP:} ALP is an approximate method as opposed to LP. Thus, it is important for us to characterize the approximation error. In the context of ALP for MDPs, we care about two error terms namely the \emph{prediction error} $\norm{\tj-J^*}$, that captures the error in the approximate value function $\tj$ and the \emph{control error} $\norm{J_{\tu}-J^*}$, that is the loss in performance when a sub-optimal policy $\tu$ is used instead of an optimal policy $u^*$ (note that here $\norm{\cdot}$ is an appropriate norm).\par

>>>>

\textbf{Error Analysis of ALP:} %ALP is an approximate method as opposed to LP. Thus, it is important for us to characterize the approximation error. In the context of ALP for MDPs,
We care about two error terms namely the \emph{prediction error} $\norm{\tj-J^*}$, that captures the error in the approximate value function $\tj$ and the \emph{control error} $\norm{J_{\tu}-J^*}$, that is the loss in performance when a sub-optimal policy $\tu$ is used instead of an optimal policy $u^*$ (note that here $\norm{\cdot}$ is an appropriate norm).\par
